Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-10-21 attenuation.tex
done up to logic tree session

\myrevision{A common approach used in seismic hazard analysis given the availability of multiple GMPEs is to address the associated epistemic uncertainty through a combination of the various GMPEs. However, in comparisons not shown here for brevity, we found that some of these GMPEs yielded mean predictions that were very close to each other. In an analysis based on the LLH coefficients reported by \citet{Zafarani2014}, and using the approach of \citet{Scherbaum_2009_BSSA} we found, for instance, that a logic-tree partition for the GMPEs proposed by \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, leads to weights of 0.3376, 0.3354, and 0.3270, respectively. These results meant that neither of these GMPEs had a substantial advantage over the others. This, however, would go against the desired to account for the associated uncertainty. Recently, \citet{Atkinson2014} argued that in such cases where multiple GMPEs do not offer sufficient variability, their combination does not necessarily and properly address uncertainty and suggests that, instead, one can better consider a high and low alternative based on a central backbone model. Fig.~\ref{fig:att} illustrates the variation of horizontal PGA components (in g) with distance obtained using four of the GMPEs mentioned before for two different earthquake magnitudes. In these and other similar comparisons we noticed that the GMPE proposed by \citet{Kalkan2004} led to centered prediction and we chose this particular GMPE as our central backbone and define an upper and lower bound as the two alternative GMPEs in our logic tree analysis, such that---for the most part---the amplitudes predicted by the mean values of other GMPEs fell within the range of defined by these bounds.}

>>>>

\myrevision{A common approach used in seismic hazard analysis given the availability of multiple GMPEs is to address the associated epistemic uncertainty through a combination of the various GMPEs. However, in comparisons not shown here for brevity, we found that some of these GMPEs yielded mean predictions that were very close to each other. In an analysis based on the LLH coefficients reported by \citet{Zafarani2014}, and using the approach of \citet{Scherbaum_2009_BSSA} we found, for instance, that a logic-tree partition for the GMPEs proposed by \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, leads to weights of 0.3376, 0.3354, and 0.3270, respectively. These results meant that neither of these GMPEs had a substantial advantage over the others. This, however, would go against the desired to account for the associated uncertainty. Recently, \citet{Atkinson2014} argued that in such cases where multiple GMPEs do not offer sufficient variability, their combination does not necessarily and properly address uncertainty and suggests that, instead, one can better consider a high and low alternative based on a central backbone model. Fig.~\ref{fig:att} illustrates the variation of horizontal PGA components (in g) with distance obtained using four of the GMPEs mentioned before for two different earthquake magnitudes. In these and other similar comparisons we noticed that the GMPE proposed by \citet{Kalkan2004} led to centered prediction and we chose this particular GMPE as our central backbone and defined an upper and lower bound (plus and minus one standard deviation) as the two alternative GMPEs in our logic tree analysis, such that---for the most part---the amplitudes predicted by the mean values of other GMPEs fell within the range of defined by these bounds.}
